---
title: "Weight of Fish"
author: "Cadence Gorden"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(leaps)
library(car)
```
```{r}
Fish<- read_csv(file="Fish.csv") 
```



# Predicting Fish Weight


## Perch
```{r}
Perch<-filter(Fish, Species=="Perch")
Perch<-select(Perch, -Species)
```



### Best Models
```{r}
regsubsets.out <-
    regsubsets(Weight ~ .,
             data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Two regressor model
```{r}
Perchmode<-lm(Weight~Height+Width,data=Perch)
summary.lm(Perchmode)
```
Through filtering out the perch fish and only using numerical variables, we determined 
the best subset is the height and width and the best 2 subset is also the height and width

## Bream
```{r}
Bream<-filter(Fish, Species=="Bream")
Bream<-select(Bream, -Species)
```

### Best Models
```{r}
regsubsets.out <-
    regsubsets(Weight ~ .,
             data = Bream,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Two regressor model
```{r}
Breammode<-lm(Weight~Height+Width+Length1,data=Bream)
summary.lm(Breammode)
```
Through filtering out the Bream fish and only using numerical variables, we discovered that the best subset is height, width, and length1. The best 2 subset was length2 and height. 

## Roach
```{r}
Roach<-filter(Fish, Species=="Roach")
Roach<-select(Roach, -Species)
```
### Best Models
```{r}
regsubsets.out <-
    regsubsets(Weight ~ .,
             data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
### Best Two regressor model
```{r}
Roachmode<-lm(Weight~Length3+Width,data=Roach)
summary.lm(Roachmode)
```
Through filtering out the Roach fish and only using numerical variables, we found that length3 and width were the best subset as well as the the best 2 subset. 

## Final Summary Statements
By using the leap formula, we learned how to do multiple linear regression. We filtered the perch, bream, and roach fish into their own files. The perch fishes best subsets were the height and width as well as their best 2 subset was height and width. The breams best subset was height, length1, and width and the best 2 subset was length2 and height. Roaches best subset was width and length 3, the best 2 subset was the same as the best subset. 
